Information Distribution Depends on Language-Specific Features

### 2019-01-30 cogsci/position-info.Rmd
cogsci reorganization

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as @levy2007 and @jaeger2010, the Switchboard corpus of adult telephone conversations. We also examine child-adult conversations in the CHILDES TalkBank [@brown1973; @macwhinney2014] corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus.

@@

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$
With this measure, @yu2016  compute the unigram entropy at each position of sentences of each length within the corpus. The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances. @genzel2002 similarly examine a unigram entropy measure on sentences, and found that entropy at the sentence level increases linearly with sentence index within a corpus. UID applies this uniformity of entropy rate in sentences to all levels of speech, and so the @yu2016, which examines text at the word level, should find an affine function at the word level.

@@

entropies <- map(2:10, ~unigram_entropy(.x, sb_tokens)) %>%
  bind_rows()

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F)
```

We used the Providence English corpus from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

@@

# Written data

>>>>

```{r our_replication, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Providence corpus unigram entropy"}

img <- png::readPNG("figs/Prov_corpus_result.png")
grid::grid.raster(img)
```

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as @levy2007 and @jaeger2010, the Switchboard corpus of adult telephone conversations. We also examine child-adult conversations in the CHILDES TalkBank [@brown1973; @macwhinney2014] corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus. Finally, we extend our cross-linguistic findings on a small number of languages from the CHILDES experiment to a direct comparison of several dozen languages in Wikipedia.

## General methods

@@

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$

With this measure, @yu2016 compute the unigram entropy at each position of sentences of each length within the corpus. The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances. @genzel2002 similarly examine a unigram entropy measure on sentences, and found that entropy at the sentence level increases linearly with sentence index within a corpus. UID applies this uniformity of entropy rate in sentences to all levels of speech, and so the @yu2016, which examines text at the word level, should find an affine function at the word level.

The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

# Experiment 1

We first used the same source for data as @levy2007, the Switchboard corpus of American telephone conversations @godfrey1992.

@@

entropies <- map(c(5, 7, 9), ~unigram_entropy(.x, sb_tokens)) %>%
  bind_rows()

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  ggtitle("Representative Switchboard Entropy Curves Faceted on Utterance Length") + 
  xlab("Word Order within Utterance") +
  ylab("Positional Entropy") +
  scale_x_discrete(limits = "1":"9") + 
  geom_pointrange() +
  geom_smooth(se = F)
```

# Experiment 2

We used the Providence English corpus from CHILDES. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora.We divided the corpus by speaker into child and non-child categories. We further divided the corpus by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position. Computation of positional entropy was identical to the Switchboard method after dividing for utterance length.

@@

# Experiment 3

### 2019-01-30 cogsci/position-info.tex
cogsci reorganization

\title{Information is Not Communicated Uniformly: Evidence from Spoken and
Written Corpora}

@@

\begin{abstract}
We provide evidence against the popular Uniform Information Density
hypothesis (Levy \& Jaeger, 2007) which proposes that information is
transmitted at a constant rate close to channel capacity in human
communication. Using a method based on the original Genzel \& Charniak
(2002) entropy measure, we construct a word-level model for entropy
applicable to both spoken and written corpora. We apply this model to
corpora from Wikipedia in well over a hundred languages. We find that
the Uniform Information Density hypothesis does not predict the outcome
of our word-level entropy model, but also that the by-word entropy
distribution of a language is related to the typological features of the
language. We use this evidence to suggest that people do not communicate
information at a uniform rate, but that information distribution varies
from language to language based on phonogical, morphological and
syntactic features.

@@

These theories model the process of communication as transmission of
information over a noisy channel. The producer begins with an intended
meaning, packages this meaning into a linguistic format, and then sends
it to the receiver over a communcative channel. The receiver must then
decode from the signal they receive on their end of the chanel the
producer's intended meaning. The problem is that the channel is noisy,
and sometimes the signal can get corrupted (e.g.~the producer can
misspeak, or the receiver can mishear). In order to maximize the
probability that the correct meaning is transmitted, these theories
predict that producers should choose linguistic messages that keep the
rate of information across words constant. The intuition is that if the
receiver misperceives a word, and that word contains most of the
information in the sentence, then the communication will have failed.
Because producers cannot predict which word a speaker will mishear,
their best strategy is spread the information evenly across all of the
words in a sentence, i.e.~maintain \emph{uniform information density}
(Genzel \& Charniak, 2002; R. P. Levy \& Jaeger, 2007).

@@

However, other recent work has contradicted the UID hypothesis. Similar
to the original R. P. Levy \& Jaeger (2007), Zhan \& Levy (2018) focuses
on information distribution at particular points in sentences. Zhan \&
Levy (2018) finds that more information-rich classifiers in Mandarin
Chinese are produced when production of the neighboring noun is
difficult, not when the information content is high. On a sentential
level, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) examine word
order across spoken sentences in Hindi, a freer word order language than
English, and find that information density has no significant effect on
word order.

Recently, Yu, Cong, Liang, \& Liu (2016) developed a more direct test of
the Uniform Information Density hypothesis, applying the logic used by
Genzel \& Charniak (2002) to look at the distribution of information
\emph{within} individual sentences. Because people process language
incrementally--using the previous words in a sentence to predict the
words that will come next, the amount of information that a word
contains when seen in isolation should increase over the course of a
sentence. Analyzing a large corpus of written English, they find a
different pattern: Entropy increases over the first few words of an
utterance and then remains constant until the final word where it again
jumps up (see Figure \ref{fig:our_replication}). Yu et al. (2016)
conclude that the Uniform Information Density hypothesis must not hold
for medial words in a sentence.

We extend and generalize Yu et al. (2016) in three ways: we confirm that
this same pattern is found in spoken English--in both adult and child
speakers. We then examine entropy curves cross-linguistically, finding a
diversity of shapes across the world's languages. Finally, we show that
entropy curves are predictable from the structure of individual
languages, namely word order. Taken together, our results suggest a
refinement of the Uniform Information Density hypothesis: Speakers may
choose to order words in order to preserve uniform information, but they
must do so under prior constraints on word order imposed by the language
they speak.

@@

@@

Switchboard {[}To be put in{]}

We used the Providence English corpds from CHILDES. The Providence
corpus recorded interactions between children between 1 and 3 years old
and their parents in the home. We divided the corpus by speaker into
child and non-child categories. We further divided the corpus by
utterance length, so that all sentences of length \(k\) (e.g. \(6\))
were grouped together. Finally, within each utterance length, we
computed the unigram entropy measure for each position.

@@

We also ran this analysis on Spanish and Mandarin corpora from CHILDES.
We used the Shiro corpus for Spanish (Shiro, 2000), which contains
prompted narratives individually collected from over a hundred
Venezualan schoolchildren, half from high SES backgrounds and half from
low SES backgrounds. We used the Zhou dinner corpus for Mandarin Chinese
(Li \& Zhou, 2015), which contains dinner conversations between 5 to
6-year-old children and their parents collected in Shanghai.

For each corpus, we accessed transcripts of the corpus provided through
the TalkBank system and computed over Roman alphabet transcriptions or
transliterations of the original transcriptions. For Mandarin, we used
pinyin transliterations of the utterances in the corpus with demarcated
word boundaries, and for Japanese we used romanji (Roman alphabet)
transliterations of words in the corpus. The Chinese characters used for
writing Mandarin do not normally demarcate word boundaries by spacing
words apart, and for normal Chinese writing including spaces between
word boundaries can have a negative effect on reading times (Bai et al,
2008).

@@

\section{Written data}\label{written-data}

@@

\subsection{Methods}\label{methods-1}

Using Giuseppe Attardi's Wikiextractor tool
\footnote{https://github.com/attardi/wikiextractor}, we extracted the
text corpora for \(165\) languages from Wikipedia by downloading a
stored collection of Wikipedia entries in each langauge and randomly
selecting several thousand articles from each Wikipedia language. Each
language corpus was cleaned and limited to sentences between \(6\) and
\(50\) words. Similar to our process for the Switchboard and CHILDES
spoken corpora, we divided each corpus by sentence length, and then
computed the unigram entropy measure on each word position within each
sentence length. We wanted to directly compare and classify the unigram
entropy curves of the languages from Wikipedia. We computed three slope
treatments of each curve. In the \emph{absolute} treatment, with
sentence length denoted as \(n\), we computed the slope between
positions \(1\) and \(2\), positions \(2\) and \(3\), positions \(3\)
and \(n-2\), positions \(n-2\) and \(n-1\) and positions \(n-1\) and
\(n\). For the short utterances appearing the CHILDES speech corpora we
examined, these appeared to be important junctions in the distributions,
with a seeming plateau in the middle of the unigram entropy curve for
each of the language corpora we examined in CHILDES.

@@

{[}Put in an illustration of the slope sections and treatments here?{]}

@@

In the \emph{absolute} and \emph{relative 5} treatments, each language
is embedded in \(5\)-dimensional space. In the \emph{relative 10}
treatment, each language is embedded in \(10\)-dimensional space. This
allows for direct comparison between languages on Wikipedia using cosine
similarity and moreover for unsupervised clustering analysis to compare
the results of the Wikipedia entropy analysis to known typological
features within the langauges in the Wikipedia dataset. To determine
which phonological, morphological and syntactic features affected the
embedding of a language in the Wikipedia dataset, we looked at the list
of \(144\) linguistic features in World Atlas of Language Structures
(Dryer \& Haspelmath, 2013). We limited the languages in the WALS
database to only those in our Wikipedia dataset and performed
missing-value imputation to obtain the features not coded in WALS for
the languages from Wikipedia.

One approach is to cluster the languages used in the Wikipedia analysis
on the basis of WALS features and then directly compare the WALS
clustering results with the results of the hierarchical clustering on
the Wikipedia slope data for each of the different treatments using
clustering similarity evaluation methods such as the Rand index (Rand,
1971). However, the problem then arises of which combination of WALS
features and how many features to include in the clustering analysis.
This is a computationally intractable operation. Additionallly, deciding
how many clusters to use in an unsupervised clustering analysis is an
unsolved problem in machine learning.

@@

Cosine distance played some role in the feature determination. The top
features were \(83\), \(81\), \(95\) and \(97\), which all characterize
word order. This makes intuitive sense, and indicates that for this
small subset of features and subset of languages that the embeddings in
the slope space are related to the WALS features. Therefore typological
features play a role in determining the positional entropy values for a
language. This means that the entropy curves are in some way structured
by the syntactic, morphological and phonological features of a language.

\section{Conclusions}\label{conclusions}

In this paper, we have characterized and applied a model based on Genzel
\& Charniak (2002) for distinguishing entropy at each word position
within sentences. In doing so, we have provided evidence against the
Uniform Information Density hypothesis. Our work indicates that
information is not distributed uniformly throughout an utterance
regardless of languages, but that languages possess a characteristic
information distribution determined by their syntactic, morphological
and phonological features.

Our work has focused on words within sentences in both speech and text
across typologically diverse languages. Other researchers have explored
information rate cross-linguistically as a single number characterizing
each language, most notably including Aylett \& Turk (2004). That work
characterizes information rate as information per unit time, and is
complementary to the work we accomplish here. Languages may possess both
an overall information transfer rate, showing the average amount of
semantic information transmitted per syllable or word, and an entropy
distribution indicative of the language's information distribution.

Research has indicated the effects of surprisal on fixation duration
during eye-tracking studies (Demberg \& Keller, 2008) (Boston et al.,
2008) (Smith \& Levy, 2013). Higher surprisal of a word is on average
predictive of higher fixation duration. The \emph{wrap-up effect} states
that when a person reads written text, he or she will process
sentence-final words more slowly on average then sentence-medial or
sentence-initial words, due to integrating information from the entire
sentence to form a final understanding of the sentence's meaning (Stowe
et al., 2018) (Kuperman et al., 2010). The wrap-up effect is drawn from
evidence in English, German and Dutch, all of which are languages with a
large final increase in their entropy curve from our study. We aim to
see in the future if as a consequence of our work in this paper, the
wrap-up effect falls out from the final jump in the entropy curves in
some languages. We would analyze eye-tracking data from languages with
low positional entropy in sentence-final positions. Since the lexical
surprisal metric in eye-tracking and our positional entropy metric are
both measures of log-probability surprisal, then in languages such as
Hindi where the sentence-final positional entropy values are low we
expect to find no wrap-up effect.

@@

@@

@@

@@

@@

>>>>

\title{Information Distribution Depends on Language-Specific Features}

@@

\begin{abstract}
We argue for a reformulation of the Uniform Information Density
hypothesis R. P. Levy \& Jaeger (2007) in which the grammatical,
phonological and morphological features of a language determine how
information is distributed throughout utterances. We expand on a method
from Yu, Cong, Liang, \& Liu (2016) to compute entropy based on word
position within utterances as a derivation of information distribution.
We analyze adult and child spoken corpora as well as text corpora drawn
from a variety of languages on Wikipedia. We find that each language has
a robust, characteristic entropy curve across word position, and present
evidence that these entropy curves are in part determined by typological
features. We conclude that speakers may tend towards communicating
information uniformly, but the distribution of information in their
utterances is conditioned on the language they communicate in.

@@

These theories model the process of communication as transmission of
information over a noisy channel. The producer begins with an intended
meaning, packages this meaning into language, and then sends the meaning
to their intended receiver over a communcative channel. The receiver
must then decode from the signal they receive on their end of the
channel the producer's intended meaning. The problem is that the channel
is noisy, and sometimes the signal can get corrupted (e.g.~the producer
can misspeak, or the receiver can mishear). In order to maximize the
probability that the correct meaning is transmitted, these theories
predict that producers should choose linguistic messages that keep the
rate of information across words constant. The intuition is that if the
receiver misperceives a word, and that word contains most of the
information in the sentence, then the communication will have failed.
Because producers cannot predict which word a speaker will mishear,
their best strategy is spread the information evenly across all of the
words in a sentence, i.e.~maintain \emph{uniform information density}
(Genzel \& Charniak, 2002; R. P. Levy \& Jaeger, 2007).

@@

However, other recent work has contradicted the UID hypothesis. Similar
to the original R. P. Levy \& Jaeger (2007), Zhan \& Levy (2018) focuses
on information distribution at particular points in sentences. Zhan \&
Levy (2018) finds that more information-rich classifiers in Mandarin
Chinese are produced when production of the neighboring noun is
difficult, not when the information content is high. Jain, Singh,
Ranjan, Rajkumar, \& Agarwal (2018) examine word order across spoken
sentences in Hindi, a freer word order language than English, and find
that information density has no significant effect on word order.

Recently, Yu et al. (2016) developed a more direct test of the Uniform
Information Density hypothesis, applying the logic used by Genzel \&
Charniak (2002) to look at the distribution of information \emph{within}
individual sentences. Because people process language
incrementally--using the previous words in a sentence to predict the
words that will come next--the amount of information that a word
contains when seen in isolation should increase over the course of a
sentence. Analyzing a large corpus of written English, they find a
different pattern: Entropy increases over the first few words of an
utterance and then remains constant until the final word where it again
jumps up (see Figure \ref{fig:our_replication}). Yu et al. (2016)
conclude that the Uniform Information Density hypothesis must not hold
for medial words in a sentence.

{\centering \includegraphics{figs/our_replication-1}

\caption[Providence corpus unigram entropy]{Providence corpus unigram entropy}\label{fig:our_replication}
\end{figure*}
\end{CodeChunk}

We extend and generalize Yu et al. (2016) in three ways: we confirm that
this same pattern is found in spoken English--in both adult and child
speakers. We then examine entropy curves cross-linguistically, finding a
diversity of shapes across the world's languages. Finally, we show that
entropy curves are predictable from the structure of individual
languages, namely word order. Taken together, our results suggest a
refinement of the Uniform Information Density hypothesis: speakers may
structure their utterances to optimize information density, but they
must do so under the constraints of the language they use to
communicate.

@@

\section{Experiment 1}\label{experiment-1}

@@

\section{Experiment 2}\label{experiment-2}

We used the Providence English corpus from CHILDES. The Providence
corpus recorded interactions between children between 1 and 3 years old
and their parents in the home. We divided the corpus by speaker into
child and non-child categories. We further divided the corpus by
utterance length, so that all sentences of length \(k\) (e.g. \(6\))
were grouped together. Finally, within each utterance length, we
computed the unigram entropy measure for each position.

@@

We also ran this analysis on Spanish and Mandarin corpora from CHILDES.
We used the Shiro corpus for Spanish Shiro (2000), which contains
prompted narratives individually collected from over a hundred
Venezualan schoolchildren, half from high SES backgrounds and half from
low SES backgrounds. We used the Zhou dinner corpus for Mandarin Chinese
(Li \& Zhou, 2015), which contains dinner conversations between 5 to
6-year-old children and their parents collected in Shanghai.

For each corpus, we accessed transcripts of the corpus provided through
the TalkBank system and computed over the Latin alphabet transcriptions
or transliterations of the original transcriptions. For Mandarin, we
used pinyin transliterations of the utterances in the corpus with
demarcated word boundaries. The Chinese characters used for writing
Mandarin do not normally demarcate word boundaries by spacing words
apart, and for normal Chinese writing including spaces between word
boundaries can have a negative effect on reading times Bai, Yan,
Liversedge, Zang, \& Rayner (2008).

@@

\section{Experiment 3}\label{experiment-3}

@@

Using Giuseppe Attardi's Wikiextractor tool
\footnote{https://github.com/attardi/wikiextractor}, we extract text
corpora from Wikipedia by downloading a stored collection of Wikipedia
entries in each langauge and randomly selecting several thousand
articles from each Wikipedia language. Each language corpus was cleaned
and limited to sentences between \(6\) and \(50\) words. Similar to our
process for the Switchboard and CHILDES spoken corpora, we divided each
corpus by sentence length, and then computed the unigram entropy measure
on each word position within each sentence length. We wanted to directly
compare and classify the unigram entropy curves of the languages from
Wikipedia. We computed three slope treatments of each curve. In the
\emph{absolute} treatment, with sentence length denoted as \(n\), we
computed the slope between positions \(1\) and \(2\), positions \(2\)
and \(3\), positions \(3\) and \(n-2\), positions \(n-2\) and \(n-1\)
and positions \(n-1\) and \(n\). For the short utterances appearing the
CHILDES speech corpora we examined, these appeared to be important
junctions in the distributions, with a seeming plateau in the middle of
the unigram entropy curve for each of the language corpora we examined
in CHILDES.

@@

@@

In the \emph{absolute} and \emph{relative 5} treatments, each language
is embedded in \(5\)-dimensional space. In the \emph{relative 10}
treatment, each language is embedded in \(10\)-dimensional space. This
allows for direct comparison between languages on Wikipedia using cosine
similarity and moreover for unsupervised clustering analysis to compare
the results of our position-wise analysis on datasets from Wikipedia to
known typological features within the languages. To determine which
phonological, morphological and syntactic features affected the
embedding of a language in the Wikipedia dataset, we use the linguistic
features in World Atlas of Language Structures (Dryer \& Haspelmath,
2013).

{[}Ideally do everything, but missing values in WALS, and how to compare
every combination of features{]} An ideal approach using all of the
corpora we can download from Wikipedia and all \(144\) features from the
WALS database. Cluster the languages used in the Wikipedia analysis on
the basis of WALS features and then directly compare the WALS clustering
results with the results of the hierarchical clustering on the Wikipedia
slope data for each of the different treatments using clustering
similarity evaluation methods such as the Rand index (Rand, 1971).
However, the problem then arises of which combination of WALS features
and how many features to include in the clustering analysis. This is a
computationally intractable operation. Additionallly, deciding how many
clusters to use in an unsupervised clustering analysis is an unsolved
problem in machine learning.

@@

Cosine distance played some role in the feature determination. The top
four features all characterize word order, which indicates that for this
subset of features and languages that the embeddings in the slope space
are related to the WALS features. Therefore typological features play a
role in determining the positional entropy values for a language. This
means that the entropy curves are in some way structured by the
syntactic, morphological and phonological features of a language.

\section{Discussion}\label{discussion}

In this paper, we have extended and applied a model from Yu et al.
(2016) and derived from Genzel \& Charniak (2002) for distinguishing
entropy at each word position within sentences. We have argued that the
outcomes of this model are derived from the information distribution of
a language. As this model varies cross-linguistically in terms of

Follow-up with WALS features using missing-value imputation. However
here are some of the problems with that.

Our work complements the approach of studies such as Aylett \& Turk
(2004), where languages are characterized by a rate of semantic
information per syllable. This body of work attests to languages
possessing different rates of information transfer based on typological
features as well.

We also propose follow-up within linguistic processing using evidence
from cross-linguistic eye-tracking. Research has indicated the effects
of surprisal on fixation duration during eye-tracking studies (Boston,
Hale, Kliegl, Patil, \& Vasishth, 2008; Demberg \& Keller, 2008; Smith
\& Levy, 2013); higher surprisal of a word is on average predictive of
higher fixation duration. The \emph{wrap-up effect} states that when a
person reads written text, he or she will process sentence-final words
more slowly on average then sentence-medial or sentence-initial words,
due to integrating information from the entire sentence to form a final
understanding of the sentence's meaning (Kuperman, Dambacher, Nuthmann,
\& Kliegl, 2010; Stowe, Kaan, Sabourin, \& Taylor, 2018). The wrap-up
effect is drawn from evidence in languages with a large final increase
in their entropy curve from our study, so perhaps the wrap-up effect
derives from the sentence-final increase in entropy curves observed in
English and other Germanic languages.

@@

\hypertarget{ref-aylett2004}{}
Aylett, M., \& Turk, A. (2004). The smooth signal redundancy hypothesis:
A functional explanation for relationships between redundancy, prosodic
prominence, and duration in spontaneous speech. \emph{Language and
Speech}, \emph{47}(1), 31--56.

\hypertarget{ref-bai2008}{}
Bai, X., Yan, G., Liversedge, S. P., Zang, C., \& Rayner, K. (2008).
Reading spaced and unspaced chinese text: Evidence from eye movements.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{34}(5), 1277.

\hypertarget{ref-boston2008}{}
Boston, M. F., Hale, J., Kliegl, R., Patil, U., \& Vasishth, S. (2008).
Parsing costs as predictors of reading difficulty: An evaluation using
the potsdam sentence corpus. \emph{Journal of Eye Movement Research},
\emph{2}(1).

@@

\hypertarget{ref-demberg2008}{}
Demberg, V., \& Keller, F. (2008). Data from eye-tracking corpora as
evidence for theories of syntactic processing complexity.
\emph{Cognition}, \emph{109}(2), 193--210.

@@

\hypertarget{ref-kuperman2010}{}
Kuperman, V., Dambacher, M., Nuthmann, A., \& Kliegl, R. (2010). The
effect of word position on eye-movements in sentence and paragraph
reading. \emph{The Quarterly Journal of Experimental Psychology},
\emph{63}(9), 1838--1857.

@@

\hypertarget{ref-shiro2000}{}
Shiro, M. (2000). Diferencias sociales en la construcción del`` yo'' y
del`` otro'': Expresiones evaluativas en la narrativa de niños
caraqueños en edad escolar. In \emph{Lengua, discurso, texto: I simposio
internacional de análisis del discurso} (pp. 1303--1318). Visor.

@@

\hypertarget{ref-smith2013}{}
Smith, N. J., \& Levy, R. (2013). The effect of word predictability on
reading time is logarithmic. \emph{Cognition}, \emph{128}(3), 302--319.

\hypertarget{ref-stowe2018}{}
Stowe, L. A., Kaan, E., Sabourin, L., \& Taylor, R. C. (2018). The
sentence wrap-up dogma. \emph{Cognition}, \emph{176}, 232--247.
